Case for Support

### 2021-11-10 caseForSupport.tex
Sec 1 looking better and still working on Sec 2

\usepackage[colorlinks=true]{hyperref}
\usepackage{natbib}
\usepackage{apalike}
\usepackage{graphicx}

@@

A central goal of the software resource proposed here is to address this
problem, by providing Bonsai~(an experimental control software ecosystem;
Figure~\ref{fig:bonsai} and Section~\ref{sec:bonsai}) with state-of-the-art
online (and offline) data analysis methods
(Figure~\ref{fig:proposedBonsaiExtensions} and
Section~\ref{sec:toBeAddedMachineIntelligenceFunctionality}). Bonsai is
\textbf{unique} among experimental control software in that it allows people
with no programming experience to control sophisticated experiments. With the
proposed functionality to be added to Bonsai, its users will be able to use
sophisticated machine-learning methods to control their experiments and analyze
their data. This popularization of machine learning functionality will allow
scientists without computational skills to control sophisticated experiments
and analyze their data in unprecedented ways, which will most probably yield
important \textbf{advances in science}.

@@

Using the proposed Bonsai capabilities to communicate with software written in
other languages, we will integrate into Bonsai an initial set of state-of-the
art data analysis methods
(Section~\ref{sec:toBeAddedMachineIntelligenceFunctionality}). Developers of
advanced data-analysis methods should become interested in integrating their
algorithm into de Bonsai ecosystem because, which will allow their methods to
reach the wide Bonsai community. In addition this integration will enable
method developers, to easily compare the performance of of their methods with
that of other methods integrated into the Bonsai ecosystem. Method developers
witll become a new type of Bonsai users. These new users, will contribute to
the \textbf{sustainability} of the proposed resource beyond the period of
BBSRC-BBR funding.

@@

@@

@@

@@

>>>>

\usepackage[colorlinks=true]{hyperref}
\usepackage{natbib}
\usepackage{apalike}
\usepackage{graphicx}
\usepackage{verbatim}

@@

A central goal of the software resource proposed here is to address this
problem, by providing Bonsai~(an experimental control software ecosystem;
Figure~\ref{fig:bonsai} and Section~\ref{sec:bonsai}) with state-of-the-art
online (and offline) data analysis methods
(Figure~\ref{fig:proposedBonsaiExtensions} and
Section~\ref{sec:toBeAddedMachineIntelligenceFunctionality}). Bonsai is
\textbf{unique} among experimental control software in that it allows people
with no programming experience to control sophisticated experiments. Its large
and rapidly growing user base demonstrates the need of this type of software
resources. With the proposed functionality to be added to Bonsai, its users
will be able to use sophisticated machine-learning methods to control their
experiments and analyze their data. This popularization of machine learning
functionality will allow scientists without computational skills to control
sophisticated experiments and analyze their data in unprecedented ways, which
will most probably yield important \textbf{advances in science}.

@@

Developers of advanced data-analysis methods should become interested in
integrating them into de Bonsai ecosystem, which will allow their methods to
reach the wide Bonsai community. In addition this integration will enable
method developers, to easily compare the performance of their methods with
that of many methods previously integrated into the Bonsai ecosystem. Method
developers will thus become a new type of Bonsai users, which will contribute
to the \textbf{sustainability} of the proposed resource beyond the period of
BBSRC-BBR funding.

Using the proposed capabilities to communicate Bonsai with software written in
other languages, we will integrate into Bonsai an initial set of state-of-the
art behavioral and neural data analysis methods
(Section~\ref{sec:toBeAddedMachineIntelligenceFunctionality}).

@@

\textcolor{red}{Missing reference to alternatives to Bonsai}.

\textcolor{red}{\textit{Overview of past and current resource(s) in the subject
area in both the UK and abroad, including any alternative community resources
currently available. You should indicate the community size of the intended
resource and how this relates to the field in which it operates.}}

@@

\subsection{Software infrastructure to incorporate machine intelligence
functionality to Bonsai}
\label{sec:softwareInfrastructure}

\begin{comment}
Bonsai does not currently provide machine learning functionality. For instance,
the close-loop experimental control depicted in
Figure~\ref{fig:bci} cannot be currently implemented in
Bonsai. It represents the control of an experiment where a subject guides the
mouse position in a computer screen with her brain activity (Section~\ref{}).
Nodes highlighted in color require machine intelligence functionality currently
not available in Bonsai.
%
\end{comment}

A central aim of this proposal is to create software infrastructure to provide
this machine intelligence functionality to Bonsai in extensible and general
ways.

\subsubsection{Generality}

The number of current machine learning algorithms is very large and it is
continuously increasing. We intend to build a small number of machine
intelligence operators in Bonsai that can be configured to provide the
functionality of most machine learning algorithms.

For this, we will build on abstractions used in the \texttt{sickit-learn}
library. The success of this library is, to a large extent, due to its simple
and general application programming interface \citep[API;][]{buitinckEtAl13}.
%
This API consists of three complementary interfaces: an estimator interface for
building and fitting models, a predictor interface for making predictions and a
transformer interface for converting data.
%
Using only these three interfaces \texttt{scikit-learn} provides
implementations of a large number of machine learning algorithms for
dimensionality reduction, clustering, classification and regression.

Inspired by \texttt{scikit-learn}, Bonsai will have three types of operators:
estimators, predictors and transformers. Each of these operators will be
instantiated by objects implementing the corresponding interface.
%
For example, consider the close-loop system for the control of a computer
cursor with neural activity represented in Figure~\ref{fig:bci}a. The Bonsai
graphical program for this system is given in Figure~\ref{fig:bci}b. The
objects instantiating the SpikeThresholdDetector, the KiloSortSpikeSorter and
GPFAlatentsExtractor will implement the transformer interface, and the object
instantiating the TimeSeriesForestClassifier will implement the predictor
interface (Figure~\ref{fig:bci}b, top).
%
The parameters for the SpikeThresholdDetector and the KiloSortSpikeSorter will
be set manually by the user, as is commonly done in practice. The parameters of
the GPFAlatentsExtractor will be learnt offline in an unsupervised way in a
second pipeline (Figure~\ref{fig:bci}b, middle). Finally, the parameters of the
TimeSeriesForestClassifier will also be learnt offline, but in a supervised
way, in a third pipeline (Figure~\ref{fig:bci}b, bottom).

\begin{figure}
   \begin{center}
       \includegraphics[width=4in]{figures/bci.png}
       \caption{Close-loop system for controlling a computer cursor with brain activity}
     \label{fig:bci}
   \end{center}
\end{figure}

\begin{comment}
    The spike detector transforms membrane
potentials into spike sequences. The spike sorter transforms spikes squences
into lists of spikes, one list per neuron. The latents extractor transforms
multi-neuron lists of spikes into latent trajectories summarizing the
multi-neuon spiking activity.  The neural decoder predicts the next cursor
position from the latent trajectories.
\end{comment}

\begin{comment}
middl, whose output will set
As in this library,
there will be three type of machine intelligence operators in Bonsai:
%
estimator operators for building and fitting models, predictor operators for
making predictions and transformer operators for converting data. These
operators will be implemented by objects exposing the corresponding interfaces.

The estimator interface exposes a fit method for learning a model from training
data.  This method is called with training data (e.g., supplied as two arrays
X\_train and y\_train in supervised learning estimators). Its task is to run a
learning algorithm and to determine model-specific parameters from the training
data.  All supervised and unsupervised learning algorithms (e.g., for
classification, regression or clustering) will be offered as objects
implementing this interface. Machine learning tasks like feature extraction,
feature selection or dimensionality reduction will also be provided as
estimators.

The predictor interface extends the notion of an estimator by adding a predict
method that takes an array X\_test and produces predictions for X\_test, based
on the learned parameters of the estimator (we call the input to predict
“X\_test” in order to emphasize that predict generalizes to new data). In the
case of supervised learning estimators, this method typically returns the
predicted labels or values computed by the model.

Since it is common to modify or filter data before feeding it to a learning
algorithm, the transformer interface defines a transform method. It takes as
input some new data X\_test and yields as output a transformed version of
X\_test. Preprocessing, feature selection, feature extraction and
dimensionality reduction algorithms will be provided as transformers in Bonsai.

Bonsai will provide the ability to compose new
estimators from several base estimators. Composition mechanisms can be used
to combine typical machine learning workflows into a single object which is
itself an estimator, and can be employed wherever usual estimators can be used.
Composition of estimators will be done with Pipeline objects that chain multiple estimators into a single one. This is useful
since a machine learning workflow typically involves a fixed sequence of processing steps (e.g., feature extraction, dimensionality reduction, learning and making
predictions), many of which perform some kind of learning. A sequence of N such
steps can be combined into a Pipeline if the first N-1 steps are transformers;
the last can be either a predictor, a transformer or both.

\end{comment}

\subsubsection{Extensibility}

\textcolor{red}{I will start this section by saying that we are not proposing
to implement machine learning algorithms, as in \texttt{scipy.learn}, but to
integrate into Bonsai existing machine intelligence algorithms.}

Currently Bonsai has its own package manager, and its community of users have
already extended Bonsai's functionality with several contributed packages
(e.g., \ldots). However, these packages need to be written in C\#, while most
current data analysis methods are written in Python, R or Matlab. We propose to
add to Bonsai capabilities to communicate with software written in these
languages.

Fortunately, there exist software that allow C\# program
to call and be called by programs in these other languages. For the
communication of C\# programs with Python we will use
Python.NET\footnote{\href{https://github.com/pythonnet/pythonnet}{https://github.com/pythonnet/pythonnet}},
with R programs we will use
R.Net\footnote{\href{https://github.com/rdotnet/rdotnet}{https://github.com/rdotnet/rdotnet}}
and with Matlab we will use the built in Matlab .NET
interface\footnote{\href{https://uk.mathworks.com/help/matlab/matlab\_external/using-net-from-matlab-an-overview.html}{https://uk.mathworks.com/help/matlab/matlab\_external/using-net-from-matlab-an-overview.html}}.
In cases where these software cannot support some type of communication between
C\# and another language we will use the messaging library
ZeroMQ\footnote{\href{https://zeromq.org/}{https://zeromq.org/}}.

Using the previous software, we will build C\# wrappers around machine
intellgence programs written in other languages, so that these programs
implement the Estimator, Predictor or Transformer interfaces and can be
integrated into Bonsai as machine intelligence operators.

@@

\begin{comment}

@@

\end{comment}
